4-3-water-level

### 2022-02-02 4-3-water-level.Rmd
update matching syntax

```{r eval = FALSE}
climate <- weatherdata::climate_full %>%
  filter(between(stringr::str_sub(id, 7, 8), 76, 90)) %>%
  stretch() %>%
  filter(lubridate::year(date) == 2020) %>%
  tamp() %>%
  mutate(type = "climate")

river <- weatherdata::water %>%
  stretch() %>%
  select(date, Water_course_level) %>%
  rename(prcp = Water_course_level) %>% 
  tamp() %>%
  mutate(type = "river")
```

@@

```{r echo = TRUE}
res <- match_sites(river, climate,
                   temporal_var_to_match = prcp,
                   temporal_independent = climate,  
                   temporal_n_highest = 30,
                   temporal_min_match = 15)
```

>>>>

```{r}
climate <- weatherdata::climate_full %>%
  filter(between(stringr::str_sub(id, 7, 8), 76, 90)) %>%
  stretch() %>%
  filter(lubridate::year(date) == 2020) %>%
  tamp() %>%
  mutate(type = "climate")

river <- weatherdata::water %>%
  mutate(type = "river")
```

@@

```{r echo = TRUE}
res <- match_sites(
  river, climate,
  temporal_var_to_match = c("Water_course_level" = "prcp"),
  temporal_independent = "prcp",  
  temporal_n_highest = 30,
  temporal_min_match = 15
)
```
